\documentclass[8pt, a4paper]{article}
\usepackage[margin=0.5in]{geometry}

\newcommand{\npar}{\vspace{\baselineskip}}


%%%REMARKS

\usepackage{blindtext}

\usepackage[most]{tcolorbox}

\newtcbtheorem{remark}{\textbf{Remark :} }{
   coltitle=black,
   colback=brown!10,
   colframe=red!70!blue,
   detach title,
   boxrule=0pt,
   leftrule=2pt,
  attach title to upper,
   sharp corners,
   left=1mm,
}{}


\begin{document}


{\centering

\Large{\textsc{Answers to reviewer's questions on Luc Favre's PhD thesis}}

}

\npar

This document briefly sums up the conversion to \texttt{.json} format of the experimental data of the DEBORA experiment. It also presents the post-processing programs written in \texttt{python 3} to generate figures from NEPTUNE\_CFD simulations.

\npar

\section{Questions from Dirk Lucas}

\begin{itemize}
\setlength{\itemsep}{20pt}
\item \textbf{Misunderstanding regarding the HFP validation vs. the statement that it has been implemented in NCFD:}

\item \textbf{Use of "we" in the text}


\item \textbf{References numbering}

\item \textbf{Use of Kelvin instead of Celsius}

\item \textbf{Lack of comparison with NEPTUNE\_CFD}

\end{itemize}

%\begin{itemize}
%\item Re-explain it was tested outside of NEPTUNE\_CFD first (python code), the model has actually been implemented but still needs some extra numerical work
%\end{itemize}

\clearpage

\section{Questions from Emilio Baglietto}

\begin{itemize}
\setlength{\itemsep}{20pt}

\item \textbf{Scalability of R12 $\rightarrow$ PWR regarding CHF/ DNB ? Any new insight on this ? Regarding the ebullition cycle ?}

\item \textbf{Potential error on DEBORA $\phi_{w}$ $\rightarrow$ discussions with experimental team ? }

\item \textbf{Discontinuities in NCFD results presented ?}

\item \textbf{Li et al. test providing lower $T_{w}$ than Hibiki \& Ishii while theoretically having less sites ?}

\item \textbf{No inclusion of the microlayer in the growth term ? Subsequent validation of HFP at low pressure ?}

\item \textbf{Matching bubble growth at low pressure without ML term ? Surprising / Unexpected ?}

\item \textbf{New growth law of interest for low pressure boiling ?}

\item \textbf{Richenderfer \& Kossolapov : developing TBL experiments $\rightarrow$ not really treatable with fully developed flow correlations}

\item \textbf{Discussion regarding Li et al. vs. Hibiki \& Ishii NSD $\rightarrow$ fundamentally different (potential cavities vs. actually active sites) ? Discussion on nucleation site interactions}

\item \textbf{Lift-off diameter in boiling term $\rightarrow$ discussion vs. inception diameter because extra growth comes from liquid evaporating ? Double counting of the heat to the fluid + to heat change ?}


\item \textbf{Nearly no comparison on DEBORA case for HFP validation ? Only one case ?}

\item \textbf{Wall-adjacent cell values instead of bulk values ?}

\end{itemize}



\end{document}